---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggplot2wrapped

<!-- badges: start -->
<!-- badges: end -->

The goal of ggplot2wrapped is to ...

## Installation

You'll need this other GitHub only package

``` r
# remotes::install_github("visibledata/GPCDStools")
```

```{r}
library(ggplot2wrapped)
library(tidyverse)
```

Use this to collect file information. This is useful to make sure you don't just include EVERYTHING

```{r}
code_files <- get_code_file_info(c("~/Github/", "~/coding/r-projects-scrapbook/"), file_type = c(".qmd", ".R", ".Rmd"))
```

The report assumes you are looking at just one year's worth of data and it's 2025 so we filter for files created in 2025. It could also take a long time if you have lots of code files, so feel free to look at a different year.

Note that the value returned from this object contains **sensitive information** in the `function_call` argument.

```{r}
target_year <- 2025
data_geom_usage_2025 <- code_files |>
  add_geom_usage_to_files()
```

You can build your report using this function!

```{r, eval=FALSE}
data_geom_usage_2025 %>% 
  ggplot_wrapped_2025()
```

Or if that doesn't work there are lots of lovely functions for visualising your data

```{r}
make_geom_interactive_upset_chart(data_geom_usage_2025, height = 600)
```

